Survival Analysis of Questions Posted on the iFixit Answers forum

### 2018-03-10 article/draft1.Rnw
added Vitae section, added to Acknowledgements section, removed captions from figures

% Distribution of answer times
\begin{figure}[!htbp]
  \includegraphics[scale=0.5]{FIG1.pdf}
  \label{fig:answertimes}
% \caption{Distribution of response times}
\end{figure}

% Kaplan-Meier curve
\begin{figure}[!htbp]
  \includegraphics[scale=0.5]{FIG2.eps}
  \label{fig:kmcurve}
% \caption{Kaplan-Meier curve for all questions}
\end{figure}

@@

% fyi you can use scales::comma(val) to format numbers too

@@

% This table looks nice, but the code is brutal and not reproducible.  I feel compelled to point out 'xtable' or 'stargazer' for auto-generated latex tables like this using R.

% I think we should use 2 digits for coefficients and 3 digits for SE/p-value terms

@@

@@

This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. We also thank iFixit for providing access to the CQA data and for analysis assistance.

@@

\bibliographystyle{elsarticle-num-names}
% \bibliographystyle{plainnat}
% \bibliogrpahystyle{elsarticle-harv}

\bibliography{questions}

>>>>

% Distribution of answer times
\begin{figure}[!htbp]
  \includegraphics[scale=0.5]{FIG1.pdf}
  \label{fig:answertimes}
\end{figure}

% Kaplan-Meier curve
\begin{figure}[!htbp]
  \includegraphics[scale=0.5]{FIG2.eps}
  \label{fig:kmcurve}
\end{figure}

@@

@@

@@

\section{Vitae}

Lisa Oshita is a senior undergraduate student at the California Polytechnic State University in San Luis Obispo, majoring in statistics...

\section{Author Contributions}

All authors contributed to the analysis featured in this paper and have edited and approved of the final article.

@@

This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. This sponsor was not involved in any aspect of this paper's analysis. We also thank iFixit for providing access to the CQA data.

@@

\bibliographystyle{elsarticle-num-names}
\bibliography{questions}
